Fréchet Distance

### 2022-12-02 docs/paper.tex
generate graphics as latex pgf plot

@@

%%%
%%% Colors
%%%
\RequirePackage[table, dvipsnames]{xcolor}
\definecolor{TUGreen}{rgb}{0.517,0.721,0.094}

@@

%%%
%%% PDF
%%%

\usepackage{ifpdf}

%%% Should be LAST usepackage-call!
%%% For docu on that, see reference on package ``hyperref''
\ifpdf%   (definitions for using pdflatex instead of latex)

  %%% graphicx: support for graphics
  \usepackage[pdftex]{graphicx}

  \pdfcompresslevel=9

@@

  %%% provide all graphics (also) in this format, so you don't have
  %%% to add the file extensions to the \includegraphics-command
  %%% and/or you don't have to distinguish between generating
  %%% dvi/ps (through latex) and pdf (through pdflatex)
  \DeclareGraphicsExtensions{.pdf}

\else %else   (definitions for using latex instead of pdflatex)

  \usepackage[dvips]{graphicx}

  \DeclareGraphicsExtensions{.eps}

  \usepackage[%
    dvips,           %% sets up hyperref for use with the dvips driver
    colorlinks=false %% better for printout version; almost every hyperref-extension is eliminated by using dvips
  ]{hyperref}

\fi

@@

Besides the previously mentioned applications, 
where the course of the curves is important, 
the Fréchet distance also finds applications in
(online) signature verification \cite{zheng_algorithm_2008,fang_research_2018},
map-matching tracking data for traffic control, routing and navigation \cite{wenk_addressing_2006,brakatsoulas_map-matching_2005},
and moving object analysis, e.g., detecting commuting patterns \cite{buchin_detecting_2011}.

@@

% TODO: Why allow it? Better algorithms?
\subsection{Weak Fréchet Distance}
\label{sec_weak_frechet_distance}
The \textit{weak Fréchet distance} (non-monotone Fréchet distance) 
slightly modifies the continuous version by allowing going backwards. 
The definition remains the same as for the continuous Fréchet distance in \autoref{def_frechet_distance}
where the monotonicity of $\alpha$ and $\beta$ is no longer required.
Note that they are still required to be continuous and have the correct starting and ending values.
% TODO: Add use cases
The weak Fréchet distance is a lower bound on the continuous Fréchet distance.
However, the Ratio between them may be arbitrarily large, 
as can be seen by the structure given in \autoref{fig_weak_frechet_distance}. \cite{alt_computing_1995}

@@

\begin{figure}[ht]
  \centering
  % TODO: Replace graphic with appropiate example
  \includegraphics[width=0.8\textwidth]{images/frechet_distance/discrete-frechet-distance-upper-bound.pdf}
  \caption[Upper bound on Fréchet distance]{
    In the case of the discrete Fréchet distance 
    one frog has to wait at either start or end $Q$
    while the other one is at the middle vertex of $P$, 
    thus requiring a minimal length of $\sqrt{d^2 + l^2}$ for any coupling.
    In contrast, a leash of length $d$ is sufficient for the continuous Fréchet distance.}
  \label{fig_frechet_distance_upper_bound_example}
\end{figure}

@@

% Free Space Diagram
\begin{figure}[ht]
  \centering
  % TODO: update figure graphics
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/frechet_distance/line_segments.pdf}
      }
      \caption{Line segments $P$ and $Q$}
      \label{fig_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/frechet_distance/free_space_single_cell.pdf}
      }
      \caption{Free space diagram}
      \label{fig_free_space_diagram_example}
  \end{subfigure}
  \caption[Free space diagram example]{
    The free space diagram \autoref{fig_free_space_diagram_example} 
    for line segments $P$ and $Q$ and distance $\varepsilon$
    from \autoref{fig_free_space_lines_example} using euclidean distance.}
  \label{fig_free_space}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  % TODO: update figure graphics
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/frechet_distance/polygonal_curves.pdf}
      }
      \caption{Polygonal curves $P$ and $Q$}
      \label{fig_complex_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/frechet_distance/free_space_polygonal_curves.pdf}
      }
      \caption{Free space diagram}
      \label{fig_complex_free_space_diagram_example}
  \end{subfigure}
  \caption[Complex free space diagram example]{
    The free space diagram \autoref{fig_complex_free_space_diagram_example} 
    for polygonal curves $P$ and $Q$ from \autoref{fig_complex_free_space_lines_example} 
    and distance $\varepsilon = 0.73$ using euclidean distance.}
  \label{fig_complex_free_space}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  % TODO: Replace graphic with appropiate example
  \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-example.pdf}
  \caption[Legal intervals on free space cell boundary]{
    Legal intervals on the boundaries of a free space cell. 
    There are at most 8 intersection points for an ellipse and a rectangle.}
  \label{fig_legal_boundary_intervals_of_a_cell}
\end{figure}

>>>>

%%% pgf plots from matplotlib tikzplotlib
\usepackage{pgfplots}
\DeclareUnicodeCharacter{2212}{−}
\usepgfplotslibrary{groupplots,dateplot}
\usetikzlibrary{patterns,shapes.arrows}
\pgfplotsset{compat=newest}

@@

%%%
%%% Colors
%%%
\definecolor{TUGreen}{rgb}{0.517,0.721,0.094}

@@

\usepackage{graphicx}

@@

@@

Besides the previously mentioned applications, 
where the course of the curves is important, 
the Fréchet distance also finds applications in
(online) handwriting signature verification \cite{zheng_algorithm_2008,fang_research_2018},
map-matching tracking data for traffic control, routing and navigation \cite{wenk_addressing_2006,brakatsoulas_map-matching_2005},
and moving object analysis, e.g., detecting commuting patterns \cite{buchin_detecting_2011}.

@@

\subsection{Weak Fréchet Distance}
\label{sec_weak_frechet_distance}
The \textit{weak Fréchet distance} (non-monotone Fréchet distance) 
slightly modifies the continuous version by allowing going backwards. 
The definition remains the same as for the continuous Fréchet distance in \autoref{def_frechet_distance}
where the monotonicity of $\alpha$ and $\beta$ is no longer required.
Note that they are still required to be continuous and have the correct starting and ending values.
% TODO: Add use cases
The weak Fréchet distance is a lower bound on the continuous Fréchet distance.
However, the Ratio between them may be arbitrarily large, 
as can be seen by the structure given in \autoref{fig_weak_frechet_distance}. \cite{alt_computing_1995}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\textwidth]{images/frechet_distance/discrete-frechet-distance-upper-bound.pdf}
  \caption[Upper bound on Fréchet distance]{
    In the case of the discrete Fréchet distance 
    one frog has to wait at either start or end $Q$
    while the other one is at the middle vertex of $P$, 
    thus requiring a minimal length of $\sqrt{d^2 + l^2}$ for any coupling.
    In contrast, a leash of length $d$ is sufficient for the continuous Fréchet distance.}
  \label{fig_frechet_distance_upper_bound_example}
\end{figure}

@@

% Free Space Diagram
\begin{figure}[ht]
  \centering
  % TODO: update figure graphics
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        % \includegraphics[width=\textwidth]{images/frechet_distance/line_segments.pdf}
        \input{images/frechet_distance/line_segments.tex}
      }
      \caption{Line segments $P$ and $Q$}
      \label{fig_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        % \includegraphics[width=\textwidth]{images/frechet_distance/free_space_single_cell.pdf}
        \input{images/frechet_distance/free_space_single_cell.tex}
      }
      \caption{Free space diagram}
      \label{fig_free_space_diagram_example}
  \end{subfigure}
  \caption[Free space diagram example]{
    The free space diagram \autoref{fig_free_space_diagram_example} 
    for line segments $P$ and $Q$ and distance $\varepsilon$
    from \autoref{fig_free_space_lines_example} using euclidean distance.}
  \label{fig_free_space}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  % TODO: update figure graphics
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        % \includegraphics[width=\textwidth]{images/frechet_distance/polygonal_curves.pdf}
        \input{images/frechet_distance/polygonal_curves.tex}
      }
      \caption{Polygonal curves $P$ and $Q$}
      \label{fig_complex_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        % \includegraphics[width=\textwidth]{images/frechet_distance/free_space_polygonal_curves.pdf}
        \input{images/frechet_distance/free_space_polygonal_curves.tex}
      }
      \caption{Free space diagram}
      \label{fig_complex_free_space_diagram_example}
  \end{subfigure}
  \caption[Complex free space diagram example]{
    The free space diagram \autoref{fig_complex_free_space_diagram_example} 
    for polygonal curves $P$ and $Q$ from \autoref{fig_complex_free_space_lines_example} 
    and distance $\varepsilon = 0.73$ using euclidean distance.}
  \label{fig_complex_free_space}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  % TODO: Replace graphic with appropiate example
  \includegraphics[width=0.3\textwidth]{images/frechet_distance/square-ellipse-intersection.pdf}
  \caption[Legal intervals on free space cell boundary]{
    Legal intervals on the boundaries of a free space cell are shown with black white dashed lines. 
    There are at most 8 intersection points for an ellipse and a rectangle.}
  \label{fig_legal_boundary_intervals_of_a_cell}
\end{figure}
